CannonRV: Measuring radial velocities with a data-driven spectral model

### 2017-04-06 paper/document.tex
Add spectral broadening part

\begin{flushleft}
The calculation of spectra radial velocities(RV) plays an important role in stellar spectroscopy. By doing cross-correlation between the data spectra and the spectral template, radial velocity of each epoch can be derived with high precision and most of the stars have smaller than one pixel shift between individual visits \cite{perez2016aspcap}. As a result, the individual visits for one star do have small but not zero RV shifts between each other. Using the traditional cross-correlation to calibrate shifts smaller than one pixel always involves interpolation, which may smooth the spectra. Thus, people are in badly need of an effective tool for small RV shifts calibration. Here we introduce CannonRV, a new RV calibration tool for small shifts based on the synthesized spectra from the Cannon, which is a data driven spectral model that has been proven to work well in APOGEE DR10 and DR12 data\cite{ness2015cannon}\cite{casey2016cannon}. By assuming the synthesized spectra from the Cannon are at rest, we use these spectra as calibration templates for each visit of every star. CannonRV obtains the RV shifts between two spectra by calculating the shift of centroid with least chi-squared method\cite{hogg2010data}, which doesn't include any interpolation or cross-correlation. CannonRV also generates a new spectra, called mixed spectra, which is the linear combination of the Cannon synthesized spectra moving one pixel left, itself and one pixel right. The mixed spectra is closer to the data spectra than the original Cannon synthesized spectra in aspect of chi-squared. We apply CannonRV on part of the DR10 and all red clump stars in DR13 and it gives us some promising results, including the RV shifts between individual visits become smaller after the calibration . The RV calibration results for the red clump stars in DR13, as well as our source code for calculating small RV shift between two spectra are available online.
\end{flushleft}

>>>>

\begin{flushleft}
The calculation of spectra radial velocities(RV) plays an important role in stellar spectroscopy. By doing cross-correlation between the data spectra and the spectral template, radial velocity of each epoch can be derived with high precision and most of the stars have smaller than one pixel shift between individual visits \cite{perez2016aspcap}. As a result, the individual visits for one star do have small but not zero RV shifts between each other. Using the traditional cross-correlation to calibrate shifts smaller than one pixel always involves interpolation, which may smooth the spectra. Thus, people are in badly need of an effective tool for small RV shifts calibration. Here we introduce CannonRV, a new RV calibration tool for small shifts based on the synthesized spectra from the Cannon, which is a data driven spectral model that has been proven to work well in APOGEE DR10 and DR12 data\cite{ness2015cannon}\cite{casey2016cannon}. By assuming the synthesized spectra from the Cannon are at rest, we use these spectra as calibration templates for each visit of every star. First, CannonRV introduces a new spectra, called mixed spectra, which is the linear combination of the Cannon synthesized spectra moving one pixel left, itself and one pixel right. By fitting the mixed spectra to the data spectra using least chi squared fitting\cite{hogg2010data}, CannonRV obtains the mixed spectra and the parameters for it. The mixed spectra is closer to the data spectra than the original Cannon synthesized spectra in aspect of chi-squared. Both the RV shifts and the broadening of the spectra can be derived from these mixed spectra parameters. We apply CannonRV on part of the DR10 and all red clump stars in DR13 and it gives us some promising results, including the RV shifts between individual visits become smaller after the calibration and the spectral broadening becomes bigger as the increase of Fiber ID. The RV calibration results for the red clump stars in DR13, as well as our source code for calculating small RV shift between two spectra are available online.
\end{flushleft}
